---
title: "Modelbuild app"
author: "Bram van Dam"
date: "August 1, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

For the course 9, "Developing Data Products", which is part of the Data science specializtion on Coursera, a web app was created with the Shiny package. The idea behind it stems from course 7 (Regression Models) in which a model had to be build for the (dependent) variable `mpg` (miles per gallon) of the `mtcars` dataset. The key question then was whether type of transmission (variable `am`, automatic of manual) is a factor that influences `mpg`. At that time, it meant just typing another model definition and evaluating the result over and over again.

But genoeg blabla for now

Some links:



## What the app does

- Bullet 1
- Bullet 2
- Bullet 3

## Example calculation

Below an example calcuation is made with `mpg` (miles per gallon) as dependent variable and `am` (transmission type) and `wt` (weight) as covariates.

Dit is nog ontzettend lelijk: te veel code en uitvoer : inperken, alleen R^2 of zo laten zien, en vermelden dat echte app meer laat zien. Plot naar volgende slide.

```{r cars, echo = TRUE}
mtcarsSelect <- mtcars[, c("mpg", "am", "wt")]
modelFit <- lm(mpg ~ ., data = mtcarsSelect)
# Show statistics of the fitted model
summary(modelFit)
# Plot predicted values (by model) against observed values
pred <- predict(modelFit)
plot(x = mtcarsSelect$mpg, y = pred, xlab = "MPG data",
     ylab = "MPG predict", bty = "n", pch = 16,
     xlim = c(10, 35), ylim = c(10, 35))

```

## Slide with Plot

```{r pressure}
plot(pressure)
```

